---
title: "House Prices"
author: "Xavier Magaña Vera"
date: "9/12/2020"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

```

## Introduction

For this project I developed a Shiny App that will tell us how does the sale price of a house is influenced by the year it was built by using the AmesHousing library.

This App creates a linear model and makes a prediction on the price depending on the year you set on the slider.

## Process

1. set the panel with the sidebar and the panel where the graph most be shown
2. create the model
3. create the prediction
4. create the plot
5. create the output so the results can be shown

## Ui.R CODE
```{r, eval=FALSE, echo=TRUE}
library(AmesHousing)
h <- make_ames()

shinyUI(fluidPage(
    titlePanel("Shiny in Data Science"),
    sidebarLayout(
        sidebarPanel(
            h3("Control Center"),
            sliderInput("slider1", "Year", 1872, 2010, 1872)
        ),
        mainPanel(
            h3("Plot"),
            plotOutput("plot"),
            h2("Predicted house price:"),
            textOutput("pred")
        )
    )
))
```

## SERVER.R CODE
```{r, eval=FALSE, echo=TRUE}
library(AmesHousing)
h <- make_ames()

shinyServer(function(input, output) {
  
    model <- lm(Sale_Price~Year_Built, data = h)
    modpred <- reactive({
      ybinput <- input$slider1
      predict(model, newdata = data.frame(Year_Built = ybinput))
    })
    output$plot <- renderPlot({
      ybinput <- input$slider1
      plot(h$Year_Built, h$Sale_Price, xlab = "Year Built",
           ylab = "Sale Price")
      abline(model, col = "blue")
      legend(25,25,c("Prediction"))
      points(ybinput, modpred())
    })
    output$pred <- renderText({
      modpred()
    })
})
```














